---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# templateflow

<!-- badges: start -->
[![R-CMD-check](https://github.com/muschellij2/templateflow/workflows/R-CMD-check/badge.svg)](https://github.com/muschellij2/templateflow/actions)
<!-- badges: end -->

The goal of templateflow is to download templates from 'Templateflow' 
(https://www.templateflow.org/), a centralized resource that 
    allows programmatic access to templates for neuroimaging studies.

## Installation

You can install the released version of templateflow from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("templateflow")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("muschellij2/templateflow")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(templateflow)
## basic example code
```

